---
title: "TableWork"
author: "Olivia Freides"
date: "2/16/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Doc for figuring out the mechanics of the sheaf structure in R:
**** Function E doesnt work, functions with thetas do not work ****

```{r}
library(tidyverse)
```

Sheaf Model from SeafCanon...
Figure 6A + 6B: 

TABLE 1 AND 2:

```{r 6a}
# Table1 <- data.frame(Sensor = c("Flight plan", NA, NA, "ATC", NA, NA, NA, NA, "RDF 1", NA, "RDF 2", NA, "Sat", NA,NA, "Field", NA, NA, NA, NA, NA,"Crash est.", NA, "Consist. rad.", "Error"), Entity = c("x", "y", "z","x","y","z","v_x","v_y","Theta1", "t","Theta2", "t","s", "s_x", "s_y","x","y","z","v_x","v_y","t","x","y", NA, NA), Case1 = c(70.662, 42.829, 11178, 70.587, 42.741, 11346, -495, 164, 77.1, 0.943, 61.3, 0.89, NA, 64.599, 44.243, 70.649, 42.753, 11220, -495, 164, 0.928, 65.00013, 44.1277, 15.7, 16.1), Case2 = c(70.663, 42.752, 11299, 70.657, 42.773, 11346, -495, 164, 77.2, 0.93, 63.2, 0.974, NA, 64.63, 44.287, 70.668, 42.809, 11431, -495, 164, 1.05, 64.2396, 44.3721, 11.6, 17.3), Case3 = c(70.612, 42.834, 11237, 70.617, 42.834, 11236, -419, 310, 77.2, 0.985, 63.3, 1.05, NA, 62.742, 44.55, 70.626, 42.814, 11239, -419, 311, 1.02, 65.3745, 45.6703, 152, 193), Units = c("W", "N", "m", "W", "N", "m", "km/h W", "km/h N", "true N", "h", "true N", "h", NA, "W", "N", "W", "N", "m", "km/h W", "km/h N", "h","W", "N", "km", "km"))

#write_csv(Table1, "Table1.csv")


SixA <- data.frame(X = c("x","y","z","v_x","v_y","t","s","Theta1", "Theta2"), U1 = c("x","y","z", NA, NA, NA, NA, NA, NA), U2 = c("x","y","z","v_x","v_y", NA, NA, NA, NA), U3 = c("Theta1","t", NA, NA, NA, NA, NA, NA, NA), U4 = c("Theta2", "t", NA, NA, NA, NA, NA, NA, NA), U5 = c("s","Theta1", "Theta2", NA, NA, NA, NA, NA, NA), V1 = c("Theta1", NA, NA, NA, NA, NA, NA, NA, NA), V2 = c("Theta2", NA, NA, NA, NA, NA, NA, NA, NA), V3 = c("t", NA, NA, NA, NA, NA, NA, NA, NA))


SixA %>%
  pivot_longer(cols = 1:9, names_to = "sensor", values_to = "entity") %>%
  arrange(desc(sensor)) -> SixA


SixA

# SixA %>%
#   mutate(sensor = sensor) %>%
#   group_by(sensor) %>%
#   nest()  -> m

# cross2(m$data, m$data)
```


if sensor goes through function A, all entity are outputs, but also is the group of entities the senesor? So A_OUT == X here? i,e, in table 6a, SENSOR would have first row A_out.... down until function B?

    
This was wrong: return(list( Theta1 = atan2(entity[[1]] + entity[[2]]* entity[[3]] - r_1x, entity[[4]] + entity[[5]]* entity[[3]]- r_1y),t = entity[[3]]))


```{r}

entitytest <- list(entity = c("x", "y", "z", "v_x", "v_y", "t", list(s = c("s_x","s_y"))), value = c(70.649, 42.753, 11220.000, -495.000, 164.000, .928, list(s = c(.0123, 1234)))) #note that i made up values for entity test s_x and s_y, just to see if every function would run AND s
# S should = sx and sy. 


testyfn <- function(stalk) {
  #for (i in stalk[1]) { #for index in the entity column of the stalk
   # print(length(stalk[[1]])) #checkpoint for length of the list 'entity'
    for (i in 1:length(stalk[[1]])) { #
      #print(typeof(i)) #type of needs to be integer and not char. 
      #print(c(i, stalk[[1]][i])) # i here is number from 1 to length of stalk 1
    if (stalk[[1]][[i]] == "x"){ #general: if i = x we want to assocate value of x . wanted to have program figure out variables for us so we dont have to define by ourselves. 
      x <- stalk[[2]][[i]] # here x is assigned to its cell value i in column value stalk[[2]]
      x # this prints x as a check 
      #break #breaks stop program once x is found. 
      #}
    } else if (stalk[[1]][[i]] == "y"){
      y <- stalk[[2]][[i]]
    } else if (stalk[[1]][[i]] == "v_x"){
      v_x <- stalk[[2]][[i]]
    } else if (stalk[[1]][[i]] == "v_y"){
      v_y <- stalk[[2]][[i]]
    } else if (stalk[[1]][[i]] == "t"){
      t <- stalk[[2]][[i]]
    }
  }
    
  r_1x <- -73.662574
  r_1y <- 42.733838
  #x <- 3
  #y <- 5
  #v_x <- 6
  #v_y <-7
  #t <- 3
  
  # we assigned actual values to everything bc it was having an issue relating the two. 
  return(data.frame(entity = c("Theta1", "t"), value = c(atan2(x + v_x*t - r_1x, y +
                                                                 v_y*t- r_1y), t)))
}

```


```{r}
# an example of what we did before:
NotA <- function(stalk) {
  r_1x <- -73.662574
  r_1y <- 42.733838
  x <- stalk$value[stalk$entity=="x"][[1]]
  y <- stalk$value[stalk$entity=="y"][[1]]
  v_x <- stalk$value[stalk$entity=="v_x"][[1]]
  v_y <- stalk$value[stalk$entity=="v_y"][[1]]
  t <- stalk$value[stalk$entity=="t"][[1]]
  return(data.frame(entity = c("Theta1", "t"), value = c(atan2(x + v_x*t - r_1x, y +
                                                                 v_y*t- r_1y), t)))
}

```

```{r}
A <- function(stalk) {
  r_1x <- -73.662574
  r_1y <- 42.733838
  
    for (i in 1:length(stalk[[1]])) {
    if (stalk[[1]][[i]] == "x"){ #general: if i = x we want to associate value of x .
      # wanted to have program figure out variables for us so we dont have to define by ourselves. 
      x <- stalk[[2]][[i]] # x is assigned to its cell value i in column value stalk[[2]]
      x # this prints x as a check 
      #break #breaks stop program once x is found. 
    } else if (stalk[[1]][[i]] == "y"){
      y <- stalk[[2]][[i]]
    } else if (stalk[[1]][[i]] == "v_x"){
      v_x <- stalk[[2]][[i]]
    } else if (stalk[[1]][[i]] == "v_y"){
      v_y <- stalk[[2]][[i]]
    } else if (stalk[[1]][[i]] == "t"){
      t <- stalk[[2]][[i]]
    }
  }
  
  return(data.frame(entity = c("Theta1", "t"), value = c(atan2(x + v_x*t - r_1x, y +
                                                                 v_y*t- r_1y), t)))
}

B <- function(stalk) {
  r_1x <- -73.662574
  r_1y <- 42.733838

  for (i in 1:length(stalk[[1]])) {
    if (stalk[[1]][[i]] == "x"){ #general: if i = x we want to associate value of x .
      # wanted to have program figure out variables for us so we dont have to define by ourselves. 
      x <- stalk[[2]][[i]] # x is assigned to its cell value i in column value stalk[[2]]
      x # this prints x as a check 
      #break #breaks stop program once x is found. 
    } else if (stalk[[1]][[i]] == "y"){
      y <- stalk[[2]][[i]]
    } else if (stalk[[1]][[i]] == "v_x"){
      v_x <- stalk[[2]][[i]]
    } else if (stalk[[1]][[i]] == "v_y"){
      v_y <- stalk[[2]][[i]]
    } else if (stalk[[1]][[i]] == "t"){
      t <- stalk[[2]][[i]]
    }
  }
  return(data.frame(entity = c("Theta2", "t"), value = c(atan2(x + v_x*t - r_1x, y + v_y*t -
                                                             r_1y), t)))
}

# also correct. 
C <- function(stalk) {
  r_1x <- -73.662574
  r_1y <- 42.733838
  for (i in 1:length(stalk[[1]])) {
    if (stalk[[1]][[i]] == "s_x"){# this prints x as a check 
      #break #breaks stop program once x is found. 
      s_x <- stalk[[2]][[i]]
    } else if (stalk[[1]][[i]] == "s_y"){
      s_y <- stalk[[2]][[i]]
    }
    }
  return(data.frame(entity = "Theta1" , value = atan2(s_x - r_1x, s_y - r_1y)))
}


D <- function(stalk){
  r_2x <- -77.0897
  r_2y <- 38.935
  for (i in 1:length(stalk[[1]])) {
    if (stalk[[1]][[i]] == "s_x"){ 
        s_x <- stalk[[2]][[i]]
      } else if (stalk[[1]][[i]] == "s_y"){
        s_y <- stalk[[2]][[i]]
      }
  }
  return(data.frame(entity = "Theta2", value = atan2(s_x - r_2x, s_y - r_2y))) #->> entitytest
}

E <- function(stalk) {
  # s = expected location, where coordinates = y + displacement and x+ displacement from the equation, 
    ifelse(stalk[[1]][[i]] == s, 
           s <- stalk[[1]][stalk[1][[1]]==s], 
           NA)
  break
    for (i in 1:length(stalk[[1]])) {
    if (stalk[[1]][[i]] == "x"){ #general: if i = x we want to associate value of x .
      # wanted to have program figure out variables for us so we dont have to define by ourselves. 
      x <- stalk[[2]][[i]] 
      # x is assigned to its cell value i in column value stalk[[2]]
    } else if (stalk[[1]][[i]] == "y"){
      y <- stalk[[2]][[i]]
    } else if (stalk[[1]][[i]] == "v_x"){
      v_x <- stalk[[2]][[i]]
    } else if (stalk[[1]][[i]] == "v_y"){
      v_y <- stalk[[2]][[i]]
    } else if (stalk[[1]][[i]] == "t"){
      t <- stalk[[2]][[i]]
    }
    return(data.frame(entity = c(s), value = c(c(x + v_x*t, y + v_y*t))))
  }
      # took out theta one adn theta two bc we're just getting out s. Theta one and two are predeterimed values by other fns. 
  # add s to output value if needed, Robinson said output is value = the eq but also = s_x, s_y. 
}

testE <- function(stalk){
  for (i in 1:length(stalk[[1]])) {
    ifelse(stalk[[1]][[i]] == s, s <- stalk[[1]][stalk[1][[1]]==s], NA)
  }
  return(data.frame(entity = c(s), value = c(c(x + v_x*t, y + v_y*t))))
}

babyE <- function(stalk){
  for (i in 1:length(stalk[[1]])) {
    s <- ifelse(stalk[[1]][[i]] == s, stalk[[2]][stalk[1][["s"]]], NA)
    return(s)
  }
}

ifelse((entitytest[[1]][["s"]] == c("s_x","s_y")), entitytest[[2]][entitytest[1]$entity$s], NA)
```


```{r}
#X to U2
# This is the basic structure
entitytest[[1]][entitytest[1][[1]]=="x"| entitytest[[1]]=="y"| entitytest[[1]]=="z"|entitytest[[1]]=="v_x" | entitytest[[1]] == "v_y"]

# projections are just an identity functon. You literally just pick out the element in that.
# This is a niave projection, so we grab first things. Other projections are diff.
#So R1 x R2 x R3 -> R1 and R2 and R3
pr1xpr2 <- function(stalk){ # stalk entity is stalk[[1]]

  # ok rn we're saying, a subset of stalk, look at if the first column == x 
  # I want ot get R3 and R2
  # R3 is [x,y,z], r2 is [v_x, v_y], and r1 is [t]
  # Should i break it up into r3 r2 and r1. 
  stalk[[1]][stalk[1][[1]]=="x"| stalk[[1]]=="y"| stalk[[1]]=="z"|
                    stalk[[1]]=="v_x" | stalk[[1]] == "v_y"]
  # a leading comma is subset by columns, trailing is subset by rows. 
  # This means: Looking into the stalk, accesing the entity list
  
}


#pr1 for u2 -> u1
U2_pr1 <- function(stalk){
  stalk[[1]][stalk[1][[1]]=="x"| stalk[[1]]=="y"| stalk[[1]]=="z"]
}

#pr1 for u3 -> v1, this shouldnt work yet bc we havent figured out theta storage. 
U3_pr1 <- function(stalk){
  stalk[[1]][stalk[1][[1]]=="Theta1"]
}

#pr2 for u3 -> v3
U34_pr2 <- function(stalk){
  stalk[[1]][stalk[1][[1]]=="t"]
}

#pr1 for u4 -> v2, again shiuldnt work yet.
U4_pr1 <- function(stalk){
  stalk[[1]][stalk[1][[1]]=="Theta2"]
}
```


Heres the thing:
Robinson: "The entities listed in a given sensor are those that can be derived from that sensor's data. Theta1 and Theta2 can be derived from s, so you only need to store s in that particular sensor. That's what is done in the sheaf in the paper.  Perhaps this isn't the best implementation choice as far as automation goes?"

```{r}
#Now let's figure out how to handle creating the thetas:
## Either: Create thetas from the functions that output the coordinates, and shift them to global variables inside of the original stalk


```


Six B:
On to the restriction table! :[]

```{r 6b}
# WANT IT TO LOOK LIKE:

#data.frame(SSource = U1, SDest = U2, Map = FN)

SixB <- tibble(SSource = c("X", "X", "X", "X", "U2", "U3", "U3" , "U5", "U5", "U4",
                               "U4"),
                   SDest = (c("U2", "U3", "U5", "U4", "U1", "V1", "V3",
                                                  "V1", "V2", "V3", "V2")),
                   DMap = c(pr1xpr2, A, E, B, U2_pr1, U3_pr1, U34_pr2, C, D, U34_pr2,
                           U4_pr1))
as.data.frame(SixB) -> SixB

SixB


```


If you have the same set of entities you have the same sensors:


```{r}
#for (i in SixB$DMap){
#  do.call(i, enter)
#}

#do.call(A, enter)

#alter > ncol(SixB)
```








```{r}
tibble(x=70.649,y=42.753,z=11220,v_x=-495,v_y=164,t=0.928,s_x=1.23e-2,s_y=1.23e+3) -> stalk
r_1x <- -73.662574
r_1y <- 42.733838

stalk %>% 
  mutate(theta1=atan2(s_x - r_1x, s_y - r_1y)) %>%
  select(theta1)
```


```{r}
tibble(location=tibble(x=70.649,y=42.753,z=11220),
       velocity=tibble(x=-495,y=164),
       t=0.928,
       s=tibble(x=1.23e-2,y=1.23e+3)) -> stalk2

stalk2 %>% mutate(theta1=atan2(s$x - r_1x, s$y - r_1y)) %>% select(theta1)



```



















Assignment Table;
GOAL!

```{r}
#Assignment <- as.data.frame(sensor = c(), value = c())
#flight plan = U1

Table1 <- read.csv("Assignment2.csv")

Table1 %>%
  select(Key, entity, Case1) %>% #selecting vars for ...
  group_by(Key) %>% #grouping by key for ...
  rename(value = Case1)%>% #renaming case1 to value for test.
  nest(entity = entity, value = value) -> andrea


#%>%
#  nest(StalkValue = c(entity, value))-> Assignment 


# andrea suggested I not use the nested table, bc of how it was presenting, she suggested two different columns. 
  
  



```

```{r}

SixB %>%
  left_join(andrea, by = c(SSource = "Key")) -> SixB2 # or andrea/Assigmnt

SixB2 %>%
  mutate(StalkOutput = invoke_map(.f = DMap, .x = entity))

SixB %>%
  left_join(Assignment, by = c(SSource = "Key"))%>%
  mutate(StalkOutput = map2(DMap,StalkValue,  ~ .x(.y)))
# not a dim prob. 
#this should run when everything else works...

```



